Supplementary Material for: A Rough Guide to Pre-processing High-Frequency Animal Tracking Data

### 2021-02-04 _02_filtering_data.Rmd
change to seagreen

```{r}
# define a four colour palette
pal <- RColorBrewer::brewer.pal(4, "Set1")
```

@@

```{r echo=FALSE}
# data plot
fig_outlier_remove <-
  ggplot() +
  geom_path(
    data = data_copy,
    aes(x, y),
    col = "grey",
    lwd = 0.2
  ) +
  geom_point(
    data = data_copy[500:800, ],
    aes(x, y),
    size = 0.5,
    alpha = 0.6,
    shape = 4, col = pal[4]
  ) +
  geom_point(
    data = data_copy[!data_copy[500:800, ],
      on = c("x", "y")
    ],
    aes(x, y,
      col = (in_speed >= 0.03 & out_speed >= 0.03),
      shape = (in_speed >= 0.03 & out_speed >= 0.03),
      size = (in_speed >= 0.03 & out_speed >= 0.03)
    ),
    show.legend = F,
    alpha = 1
  ) +
  geom_path(
    data = data,
    aes(x, y),
    col = "grey20",
    alpha = 1
  ) +
  scale_color_manual(values = c(pal[3], pal[1])) +
  scale_shape_manual(values = c(1, 4)) +
  scale_size_manual(
    values = c(0.2, 2)
  ) +
  ggthemes::theme_few() +
  theme(
    axis.text = element_blank(),
    axis.title = element_blank(),
    plot.title = element_text(
      face = "bold",
      margin = margin(t = 30, b = -30),
      hjust = 0.1
    )
  ) +
  coord_equal() +
  theme(plot.background = element_rect(fill = NA)) +
  labs(
    title = "(b)"
  )
```

>>>>

```{r}
# define a four colour palette
pal <- RColorBrewer::brewer.pal(5, "Set1")
pal[3] = "seagreen"
```

@@

```{r echo=FALSE}
# data plot
fig_outlier_remove <-
  ggplot() +
  geom_path(
    data = data_copy,
    aes(x, y),
    col = "grey",
    lwd = 0.2
  ) +
  geom_point(
    data = data_copy[500:800, ],
    aes(x, y),
    # size = 0.5,
    alpha = 0.6,
    shape = 4, col = pal[5]
  ) +
  geom_point(
    data = data_copy[!data_copy[500:800, ],
      on = c("x", "y")
    ],
    aes(x, y,
      col = (in_speed >= 0.03 & out_speed >= 0.03),
      shape = (in_speed >= 0.03 & out_speed >= 0.03),
      size = (in_speed >= 0.03 & out_speed >= 0.03)
    ),
    show.legend = F,
    alpha = 1
  ) +
  geom_path(
    data = data,
    aes(x, y),
    col = "grey20",
    alpha = 1
  ) +
  scale_color_manual(values = c(pal[3], pal[1])) +
  scale_shape_manual(values = c(1, 4)) +
  scale_size_manual(
    values = c(0.2, 2)
  ) +
  ggthemes::theme_few() +
  theme(
    axis.text = element_blank(),
    axis.title = element_blank(),
    plot.title = element_text(
      face = "bold",
      margin = margin(t = 30, b = -30),
      hjust = 0.1
    )
  ) +
  coord_equal() +
  theme(plot.background = element_rect(fill = NA)) +
  labs(
    title = "(b)"
  )
```
